Fusion Moves for Correlation Clustering

### 2014-11-11 paper/egpaper_for_review.tex
started to change sec. 5, and minor figure fixes

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
%
\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}
%
Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges.

@@

% \begin{center}
%     \begin{eqnarray}
%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
%     \end{eqnarray}
% \end{center}
Once we know how to fuse segmentations, the actual algorithm 
for correlation clustering 
is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
We iteratively improve the best solution by
fusing it with proposal solutions.
The inherent difference is how we define the fusion.
We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
and optimize the subproblems as described in 
Sec.\ref{sec:fast_optimization}.

>>>>

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
%
\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}
%
Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges
(see Fig.~\ref{fig:move_graph}).

@@

% \begin{center}
%     \begin{eqnarray}
%       y \cdot w \leq \min(y'\cdot w,  y'' \cdot w) 
%     \end{eqnarray}
% \end{center}
Once we know how to fuse segmentations, the actual algorithm 
for correlation clustering 
is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
We iteratively improve the best solution by
fusing it with proposal solutions.
The inherent difference is how we define the fusion.
We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}
and optimize the subproblems as described in 
Sec.~\ref{sec:fast_optimization} (see Fig. \ref{fig:move_graph}).
